---
title: "STAT143_Project"
author: "Nancy Li"
date: "2024-04-27"
output: pdf_document
---

```{r setup, include=FALSE}
# Set up
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1)
setwd("/Users/lsjnancy/Desktop/STAT143/project")
# install.packages("devtools")
devtools::install_github("ryurko/nflWAR")

# wpa_model_results_2017 = readRDS("wpa_model_results_2017.rds")
# wpa_model_results_2017
```


# Building nlfWAR

## Step 1: Get NFL data (2017)

```{r}
library(nflWAR)
library(tidyverse)

##### Step 1: Get NFL Data #####
nfl2017 = get_pbp_data(2017)
print(dim(nfl2017))
print(colnames(nfl2017))
print(head(nfl2017))
```

There are 103 variables in the file. The description of the variables can be found in this link: https://github.com/ryurko/nflscrapR-data/tree/master/legacy_data.


## Step 2: Add player positions to play-by-play data

```{r}
##### Step 2: Add player positions to play-by-play data #####
nfl2017 = add_positions(nfl2017, 2017)
print(dim(nfl2017))
nfl2017_last6 = nfl2017[, (ncol(nfl2017)-5):ncol(nfl2017)]
print(colnames(nfl2017_last6))
print(head(nfl2017_last6))
```

There are now a total of 109 variables in the data, with 6 variables added: 

1. `Passer_ID_Name`: e.g., T.Brady-00-0019596
2. `Receiver_ID_Name`: e.g., D.Allen-00-0029689
3. `Rusher_ID_Name`: e.g., J.Hekker-None
4. `Passer_Position`: e.g., QB
5. `Receiver_Position`: e.g., TE
6. `Rusher_Position`: e.g., NA

Player positions: running backs (RB), wide receiver (WR), tight end (TE), and quarterback (QB).


## Step 3: Add additional model variables to play-by-play data

```{r}
##### Step 3: Add additional model variables to play-by-play data #####
nfl2017 = add_model_variables(nfl2017)
print(dim(nfl2017))
nfl2017_last8 = nfl2017[, (ncol(nfl2017)-7):ncol(nfl2017)]
print(colnames(nfl2017_last8))
print(head(nfl2017_last8))
```

There are now a total of 117 variables in the data, with 8 variables added: 

1. `Shotgun_Ind`: Indicator whether or not the play was in shotgun.
2. `No_Huddle_Ind`: Indicator whether or not the play was no huddle.
3. `Home_Ind`: Indicator whether or not the possession team was home.
4. `airEPA_Result`: airEPA for complete passes and EPA for incomplete.
5. `airWPA_Result`: airWPA for complete passes and WPA for incomplete.
6. `yacEPA_Result`: yacEPA for complete passes and EPA for incomplete.
7. `yacWPA_Result``: yacWPA for complete passes and WPA for incomplete.
8. `Team_Side_Gap`: Combine the team, side, and run gap for O-line proxy


## Step 4: Filter the play-by-play data to data for modeling

```{r}
##### Step 4: Filter the play-by-play data to data for modeling #####
nfl2017_model_dfs = prepare_model_data(nfl2017)
pass_model_df2017 = nfl2017_model_dfs$pass_model_df
rush_model_df2017 = nfl2017_model_dfs$rush_model_df

cat("Passing play-by-play data:", dim(pass_model_df2017))
pass_model_df2017_last10 = pass_model_df2017[
  , (ncol(pass_model_df2017)-9):ncol(pass_model_df2017)]
print(colnames(pass_model_df2017_last10))
print(head(pass_model_df2017))

cat("Rushing play-by-play data:", dim(rush_model_df2017))
rush_model_df2017_last10 = rush_model_df2017[
  , (ncol(rush_model_df2017)-9):ncol(rush_model_df2017)]
print(colnames(rush_model_df2017))
print(head(rush_model_df2017))
```

There are 2 dataframes (passing model and rushing model), each with a total of 127 variables.


## Step 5: Create player tables for each position

```{r}
##### Step 5: Create player tables for each position #####
# add_position_tables(model_data_list)
# model_data_list: List of two dataframes (1) pass_model_df, (2) rush_model_df
# return List of dataframes with the given model_data_list,
# as well as the tables for each position containing player names/IDs, 
# respective number of attempts for both passing/receiving and rushing/sacks.

nfl2017_player_tables = add_position_tables(nfl2017_model_dfs)
```


## Step 6: Find replacement level for each position

```{r}
##### Step 6: Find replacement level for each position #####

# create_percentage_replacement_fn(
# 1. replacement_depth: Number indicating how many players of that position
# and performance type each team should have, then every player have that will
# be considered replacement level
# 2. positions: String indicating which position(s) to find the replacement 
# level for, can only be (1) "QB", (2) "RB" (or "FB"), (3) "WR", or (4) "TE"
# 4. attempt_type: String indicating which type of attempts to use from position
# tables to sort the players by for finding the league replacement level
# 5. combine_wrte = 0: Indicator for whether or not to combine the TE and WR 
# position tables, which will be primarily used for rushing attempts by 
# WRs and TEs (default is 0).
# )
# return: function to find percentage based replacement level QBs
# examples
# Create replacement function for RBs by stating every team has 3 RBs on their
# team for rushing, and every RB with less rushing attempts than the top 3*32 is
# considered replacement level:
# find_replacement_RB_rush=create_league_replacement_fn(3,"RB","Rush_Attempts")
# replacement_RBs = find_replacement_RB_rush(model_data_list)
# Here, our model_data_list is nfl2017_player_tables

league_replacement_functions = 
  list("find_replacement_QB" = 
         create_percentage_replacement_fn("Perc_Total_Plays", .1),
       "find_replacement_RB_rec" = 
         create_league_replacement_fn(3, "RB", "Targets"),
       "find_replacement_WR_rec" = 
         create_league_replacement_fn(4, "WR", "Targets"),
       "find_replacement_TE_rec" = 
         create_league_replacement_fn(2, "TE", "Targets"),
       "find_replacement_RB_rush" = 
         create_league_replacement_fn(3, "RB", "Rush_Attempts"),
       "find_replacement_WR_TE_rush" = 
         create_league_replacement_fn(1, "WR", "Rush_Attempts", 
                                      combine_wrte = 1))

# find_positional_replacement_level(model_data_list, replacement_fns)
# model_data_list is nfl2017_model_dfs
# replacement_fns: A list of functions to find replacement levels of 
# 1. QBs, 2. RBs for receiving plays, 3. WRs for receiving plays,
# 4. TEs for receiving plays, 5. RBs for rushing plays, 
# 6. WRs and TEs for rushing plays
# return: the input model_data_list but with replacement-level
# players' names in the play-by-play data all set to be
# Replacement_POSITION and a new column for each of the
# positional tables indicating which players are replacement
# level.

nfl2017_player_tables = find_positional_replacement_level(
  nfl2017_player_tables, league_replacement_functions)
# qb_table = nfl2017_player_tables$QB_table
# rb_table = nfl2017_player_tables$RB_table
# wr_table = nfl2017_player_tables$WR_table
# te_table = nfl2017_player_tables$TE_table
# cat("\nqb_table:", dim(qb_table))
# print(head(qb_table))
# cat("\nrb_table:", dim(rb_table))
# print(head(rb_table))
# cat("\nwr_table:", dim(wr_table))
# print(head(wr_table))
# cat("\nte_table:", dim(te_table))
# print(head(te_table))
```

## Step 7: Calculate the 3 types iPA and iPAA values for each player

```{r}
##### Step 7: Calculate the 3 types iPA and iPAA values for each player #####

### EPA-based WAR ###
## 1. Create the expected points based model formulas: ##
# e.g., (1 | Team_Side_Gap) specifies that a random intercept should be 
# included for each level of Team_Side_Gap. 
ep_model_formula_list = list(
  "air_formula" = as.formula(
    airEPA_Result ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + QBHit + 
      Receiver_Position + PassLocation + Rush_EPA_Att +
      (1|Passer_ID_Name) + (1|Receiver_ID_Name) + (1|DefensiveTeam)),
  "yac_formula" = as.formula(
    yacEPA_Result ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + QBHit +
      AirYards*Receiver_Position + PassLocation + Rush_EPA_Att +
      (1|Passer_ID_Name) + (1|Receiver_ID_Name) + (1|DefensiveTeam)),
  "qb_rush_formula" = as.formula(
    EPA ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + Pass_EPA_Att +
      (1|Rusher_ID_Name) + (1|DefensiveTeam)),
  "main_rush_formula" = as.formula(
    EPA ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + Rusher_Position + 
      Pass_EPA_Att + (1|Team_Side_Gap) + (1|Rusher_ID_Name) + (1|DefensiveTeam)))

## 2. Calculate iPA and iPAA values ##
# estimate_player_value_added(
# 1. model_data_list: nfl2017_player_tables
# 2. model_formula_list: ep_model_formula_list
# 3. return_models = 1)
# return: the original position tables from the input but add these columns:
# air_iPA: Individual player points/probability added in the air.
# yac_iPA: Individual player points/probability added after the catch.
# rush_iPA: Individual player points/probability added from rushing.
# air_iPAA: Individual player points/probability above average in the air.
# yac_iPAA: Individual player points/probability above average after the catch.
# rush_iPAA: Individual player points/probability above average from rushing.
# and the resulting models:
# air_model: Model fit for air component
# yac_model: Model fit for yac component
# qb_rush_model: Model fit for QB rushing/sacks
# main_rush_model: Model for for all non-QB rushing attempts

nfl2017_player_tables_ep = estimate_player_value_added(
  nfl2017_player_tables, ep_model_formula_list, return_models = 1)
# print("\nEP Example: QB_table and air_model")
# qb_table_ep = nfl2017_player_tables_ep$QB_table
# cat("\nQB_table:", dim(qb_table_ep))
# print(head(qb_table_ep))
# print("\nEP Air Model:")
# print(summary(nfl2017_player_tables_ep$air_model))


### WPA-based WAR ###
## 1. Create the win probability based model formulas: ##
wp_model_formula_list = list(
  "air_formula" = as.formula(
    airWPA_Result ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + QBHit +
      Receiver_Position + PassLocation + Rush_EPA_Att +
      (1|Passer_ID_Name) + (1|Receiver_ID_Name) + (1|DefensiveTeam)),
  "yac_formula" = as.formula(
    yacWPA_Result ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + QBHit +
      AirYards*Receiver_Position + PassLocation + Rush_EPA_Att +
      (1|Passer_ID_Name) + (1|Receiver_ID_Name) + (1|DefensiveTeam)),
  "qb_rush_formula" = as.formula(
    WPA ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + Pass_EPA_Att +
      (1|Rusher_ID_Name) + (1|DefensiveTeam)),
  "main_rush_formula" = as.formula(
    WPA ~ Home_Ind + Shotgun_Ind + No_Huddle_Ind + 
      Rusher_Position + Pass_EPA_Att +
      (1|Team_Side_Gap) + (1|Rusher_ID_Name) + (1|DefensiveTeam)))

## 2. Calculate iPA and iPAA values ##
nfl2017_player_tables_wp = estimate_player_value_added(
  nfl2017_player_tables, wp_model_formula_list, return_models = 1)
# print("\nWP Example: QB_table and air_model")
# qb_table_wp = nfl2017_player_tables_wp$QB_table
# cat("\nQB_table:", dim(qb_table_wp))
# print(head(qb_table_wp))
# print("\nWP Air Model:")
# print(summary(nfl2017_player_tables_wp$air_model))

```

## Step 8: Calculate above replacement level

```{r}
##### Step 8: Calculate above replacement level #####
# calculate_above_replacement(model_data_list)
# return: the input position tables with individual points/probability above 
# replacement (iPAR) columns: air_iPAR, yac_iPAR, rush_iPAR, and total_iPAR

# model_data_list: nfl2017_player_tables_ep, nfl2017_player_tables_wp

### EPA-based WAR ###
nfl2017_player_tables_ep = calculate_above_replacement(nfl2017_player_tables_ep)
# print(head(nfl2017_player_tables_ep$QB_table))

### WPA-based WAR ###
nfl2017_player_tables_wp = calculate_above_replacement(nfl2017_player_tables_wp)
```


## Step 9: Convert points / probabilities to wins

```{r}
##### Step 9: Convert points / probabilities to wins #####
library(knitr)

### EPA-based WAR: Convert Points to Wins ###
# convert_points_to_wins(model_data_list, points_per_win)
# model_data_list: nfl2017_player_tables_ep
# points_per_win: value indicating the number of points per win to use 
# (i.e., result of function calculate_points_per_win(years=2017))
points_per_win = calculate_points_per_win(years=2017)
print(paste("points_per_win:", points_per_win))
nfl2017_ep = convert_points_to_wins(nfl2017_player_tables_ep, points_per_win)
print("\n##### EPA-based WAR #####")
print("\nPlayer Tables By Position:")
qb_table_ep = nfl2017_ep$QB_table; rb_table_ep = nfl2017_ep$RB_table
wr_table_ep = nfl2017_ep$WR_table; te_table_ep = nfl2017_ep$TE_table
cat("\nQB_table:", dim(qb_table_ep))
kable(t(head(qb_table_ep, 2)))
cat("\nRB_table:", dim(rb_table_ep))
kable(t(head(rb_table_ep, 2)))
cat("\nWR_table:", dim(wr_table_ep))
kable(t(head(wr_table_ep, 2)))
cat("\nTE_table:", dim(te_table_ep))
kable(t(head(te_table_ep, 2)))
print("\nEP Air Model:")
print(summary(nfl2017_ep$air_model))
print("\nEP YAC Model:")
print(summary(nfl2017_ep$yac_model))
print("\nEP Rush Model:")
print(summary(nfl2017_ep$qb_rush_model))


### WPA-based WAR: Convert Probabilities to Wins  ###
# # convert_prob_to_wins(model_data_list)
# model_data_list: nfl2017_player_tables_wp
nfl2017_wp = convert_prob_to_wins(nfl2017_player_tables_wp)

print("\n##### WPA-based WAR #####")
print("\nPlayer Tables By Position:")
qb_table_wp = nfl2017_wp$QB_table; rb_table_wp = nfl2017_wp$RB_table
wr_table_wp = nfl2017_wp$WR_table; te_table_wp = nfl2017_wp$TE_table
cat("\nQB_table:", dim(qb_table_wp))
kable(t(head(qb_table_wp, 2)))
cat("\nRB_table:", dim(rb_table_wp))
kable(t(head(rb_table_wp, 2)))
cat("\nWR_table:", dim(wr_table_wp))
kable(t(head(wr_table_wp, 2)))
cat("\nTE_table:", dim(te_table_wp))
kable(t(head(te_table_wp, 2)))
print("\nEP Air Model:")
print(summary(nfl2017_wp$air_model))
print("\nEP YAC Model:")
print(summary(nfl2017_wp$yac_model))
print("\nEP Rush Model:")
print(summary(nfl2017_wp$qb_rush_model))

```


# Analyzing EPA-Based and WPA-Based Results

```{r}
# Combine EPA-Based WAR and WPA-BASED WAR results together #
combine_epa_wpa = function(data_ep, data_wp) {
  subset_cols = c("Player_ID_Name","air_WAR","yac_WAR","rush_WAR","total_WAR")
  WAR_ep = data_ep[, subset_cols]
  WAR_wp = data_wp[, subset_cols]
  
  WAR_columns = grepl("_WAR$", names(WAR_ep))
  names(WAR_ep)[WAR_columns] = paste0(names(WAR_ep)[WAR_columns], "_EP")
  names(WAR_wp)[WAR_columns] = paste0(names(WAR_wp[WAR_columns]), "_WP")
  
  WAR_all = left_join(WAR_ep, WAR_wp, by = "Player_ID_Name")
  return (WAR_all)
}

qb_WAR_all = combine_epa_wpa(qb_table_ep, qb_table_wp)
rb_WAR_all = combine_epa_wpa(rb_table_ep, rb_table_wp)
wr_WAR_all = combine_epa_wpa(wr_table_ep, wr_table_wp)
te_WAR_all = combine_epa_wpa(te_table_ep, te_table_wp)

positions = c("QB", "RB", "WR", "TE")
data_list = list(qb_WAR_all=qb_WAR_all, rb_WAR_all=rb_WAR_all, 
                 wr_WAR_all=wr_WAR_all, te_WAR_all=te_WAR_all)

for (i in 1:length(positions)) {
  df = data_list[[i]]
  pos = positions[i]
  print(paste0("There are ", dim(df)[1], " ", pos, "s in the 2017 season."))
}
# knable(qb_WAR_all)
```


### 1) Distributions of EPA-Based and WPA-Based WAR By Player Position

```{r plot_chunk1, fig.width=8, fig.height=8}
plot_WAR_distributions = function(data_WAR, position, plot_title) {
  print(summary(qb_WAR_all))
  
  par(mfrow = c(2, 2), oma = c(0, 0, 3, 0))
  # total
  x_range = range(c(data_WAR["total_WAR_EP"], data_WAR["total_WAR_WP"]))
  hist(data_WAR[["total_WAR_EP"]], col = rgb(1, 0, 0, 0.5), 
       xlim = c(x_range[1], x_range[2]),
       main = paste(position, "total_WAR"), xlab = "total_WAR")
  hist(data_WAR[["total_WAR_WP"]], col = rgb(0, 0, 1, 0.5), add = TRUE)
  legend("topright", legend = c("EPA-Based", "WPA-Based"), 
         fill = c(rgb(1, 0, 0, 0.5), rgb(0, 0, 1, 0.5)), cex = 0.75)
  
  # air
  x_range = range(c(data_WAR["air_WAR_EP"], data_WAR["air_WAR_WP"]))
  hist(data_WAR[["air_WAR_EP"]], col = rgb(1, 0, 0, 0.5), 
       xlim = c(x_range[1], x_range[2]),
       main = paste(position, "air_WAR"), xlab = "air_WAR")
  hist(data_WAR[["air_WAR_WP"]], col = rgb(0, 0, 1, 0.5), add = TRUE)
  legend("topright", legend = c("EPA-Based", "WPA-Based"), 
         fill = c(rgb(1, 0, 0, 0.5), rgb(0, 0, 1, 0.5)), cex = 0.75)
  
  # yac
  x_range = range(c(data_WAR["yac_WAR_EP"], data_WAR["yac_WAR_WP"]))
  hist(data_WAR[["yac_WAR_EP"]], col = rgb(1, 0, 0, 0.5), 
       xlim = c(x_range[1], x_range[2]),
       main = paste(position, "yac_WAR"), xlab = "yac_WAR")
  hist(data_WAR[["yac_WAR_WP"]], col = rgb(0, 0, 1, 0.5), add = TRUE)
  legend("topright", legend = c("EPA-Based", "WPA-Based"), 
         fill = c(rgb(1, 0, 0, 0.5), rgb(0, 0, 1, 0.5)), cex = 0.75)
  
  # rush
  x_range = range(c(data_WAR["rush_WAR_EP"], data_WAR["rush_WAR_WP"]))
  hist(data_WAR[["rush_WAR_EP"]], col = rgb(1, 0, 0, 0.5), 
       xlim = c(x_range[1], x_range[2]),
       main = paste(position, "rush_WAR"), xlab = "rush_WAR")
  hist(data_WAR[["rush_WAR_WP"]], col = rgb(0, 0, 1, 0.5), add = TRUE)
  legend("topright", legend = c("EPA-Based", "WPA-Based"), 
         fill = c(rgb(1, 0, 0, 0.5), rgb(0, 0, 1, 0.5)), cex = 0.75)
  
  mtext(plot_title, side = 3, outer = TRUE, cex = 1.5, line = 1, font = 2)
  
  par(mfrow = c(1, 1))
}

plot_WAR_distributions(qb_WAR_all,"QB","WAR Distributions: Quarterback (QB)")
plot_WAR_distributions(rb_WAR_all,"RB","WAR Distributions: Running back (RB)")
plot_WAR_distributions(wr_WAR_all,"WR","WAR Distributions: Wide Receiver (WR)")
plot_WAR_distributions(te_WAR_all,"TE","WAR Distributions: Tight End (TE)")
```


### 2) Correlations of EPA-Based and WPA-Based WAR By Player Position

```{r plot_chunk2, fig.width=8, fig.height=8}
plot_WAR_corr = function(data_WAR, plot_title) {
  par(mfrow = c(2, 2), oma = c(0, 0, 3, 0))
  WAR_list = c("total_WAR", "air_WAR", "yac_WAR", "rush_WAR")
  for (i in 1:length(WAR_list)) {
    col_ep = paste0(WAR_list[i], "_EP")
    col_wp = paste0(WAR_list[i], "_WP")
    corr = round(cor(data_WAR[[col_ep]], data_WAR[[col_wp]],
                     method = "pearson"), 4)
    plot(data_WAR[[col_ep]], data_WAR[[col_wp]], 
         main=paste0(WAR_list[i], " EPA vs WPA (corr=", corr, ")"),
         xlab=col_ep, ylab=col_wp)
    model = lm(as.formula(paste(col_wp, "~", col_ep)), data=data_WAR)
    abline(model, col = "red", lwd = 1)
  }
  mtext(plot_title, side = 3, outer = TRUE, cex = 1.5, line = 1, font = 2)
  par(mfrow = c(1, 1))
}

plot_WAR_corr(qb_WAR_all, "WAR Correlations: Quarterback (QB)")
plot_WAR_corr(rb_WAR_all, "WAR Correlations: Running back (RB)")
plot_WAR_corr(wr_WAR_all, "WAR Correlations: Wide Receiver (WR)")
plot_WAR_corr(te_WAR_all, "WAR Correlations: Tight End (TE)")

```


### 3) Top 10 Players Based on total_WAR By Player Position

```{r plot_chunk3, fig.width=10, fig.height=8}
# Top 10 players based on total WAR

# Order data by descending order to match the plot's bottom-to-top fill
library(ggplot2)
library(patchwork)

plot_top10_players = function(positions, margins_rt, data_list, 
                             plot_title, ep=TRUE) {
  plot_list = list()
  for (i in 1:length(positions)) {
    data_all = data_list[[i]]
    data_top10 = head(data_all[order(-data_all[["total_WAR_EP"]]),], 10)
    if (ep==TRUE) {
      data_top10 = data_top10[c("Player_ID_Name", "air_WAR_EP",
                              "yac_WAR_EP","rush_WAR_EP")]
      data_long = pivot_longer(data_top10, cols = -Player_ID_Name, 
                                names_to = "Component", 
                                values_to = "WAR")
      p = ggplot(data_long, aes(x = Player_ID_Name, y = WAR, fill = Component)) +
        geom_bar(stat = "identity", position = "stack") +
        labs(title = paste(positions[i], "WAR_EP"), 
             x = "Player_ID_Name", y = "WAR") +
        ylim(min(data_all[["total_WAR_EP"]]) - margins_rt[i], 
             max(data_all[["total_WAR_EP"]]) + margins_rt[i]) +
        coord_flip() + # Flip coordinates for horizontal bars +
        theme_minimal() +
        scale_fill_brewer(palette = "Pastel1") + 
        theme(legend.position = "bottom", legend.key.size = unit(0.5, "cm"), 
              legend.text = element_text(size = 8), 
              legend.title = element_text(size = 0, face = "bold"))
      # p = ggplot(data_top10, aes(x = reorder(Player_ID_Name, total_WAR_EP), 
      #                    y = total_WAR_EP)) +
      #   geom_bar(stat = "identity", position = "dodge", fill = "lightblue") +
      #   ylim(min(data_all[["total_WAR_EP"]]), 
      #        max(data_all[["total_WAR_EP"]]) + margins_rt[i]) +
      #   coord_flip() + # Flip coordinates for horizontal bars +
      #   geom_text(aes(label = round(total_WAR_EP, 4), hjust = -0.1), 
      #             color = "black", size = 3) +
      #   labs(title = paste(positions[i], "total_WAR_EP"), 
      #        x = "Player_ID_Name", y = "total_WAR_EP") + 
      #   theme_minimal()
    } else {
      data_top10 = data_top10[c("Player_ID_Name", "air_WAR_WP",
                              "yac_WAR_WP","rush_WAR_WP")]
      data_long = pivot_longer(data_top10, cols = -Player_ID_Name, 
                                names_to = "Component", 
                                values_to = "WAR")
      p = ggplot(data_long, aes(x = Player_ID_Name, y = WAR, fill = Component)) +
        geom_bar(stat = "identity", position = "stack") +
        labs(title = paste(positions[i], "WAR_WP"), 
             x = "Player_ID_Name", y = "WAR") +
        ylim(min(data_all[["total_WAR_WP"]]) - margins_rt[i], 
             max(data_all[["total_WAR_WP"]]) + margins_rt[i]) +
        coord_flip() + # Flip coordinates for horizontal bars +
        theme_minimal() +
        scale_fill_brewer(palette = "Pastel1") + 
        theme(legend.position = "bottom", legend.key.size = unit(0.5, "cm"), 
              legend.text = element_text(size = 8), 
              legend.title = element_text(size = 0, face = "bold"))
      # p = ggplot(data_top10, aes(x = reorder(Player_ID_Name, total_WAR_WP), 
      #                    y = total_WAR_WP)) +
      #   geom_bar(stat = "identity", position = "dodge", fill = "lightpink") +
      #   ylim(min(data_all[["total_WAR_WP"]]), 
      #        max(data_all[["total_WAR_WP"]]) + margins_rt[i]) +
      #   coord_flip() + # Flip coordinates for horizontal bars +
      #   geom_text(aes(label = round(total_WAR_WP, 4), hjust = -0.1), 
      #             color = "black", size = 3) +
      #   labs(title = paste(positions[i], "total_WAR_WP"), 
      #        x = "Player_ID_Name", y = "total_WAR_WP") + 
      #   theme_minimal()
    }
    
    plot_list[[i]] = p
  }
  
  # Combine the plots
  combined_plot = plot_list[[1]]+plot_list[[2]]+plot_list[[3]]+plot_list[[4]] + 
    plot_layout(ncol = 2) +
    plot_annotation(
      title = plot_title,
      theme = theme(
        plot.title = element_text(size = 20, face = "bold", hjust = 0.5)
      )
    )
  print(combined_plot)
}

positions = c("QB", "RB", "WR", "TE")
margins_rt = c(1, 0.5, 0.5, 0.1)

top10_players_ep = plot_top10_players(positions, margins_rt, data_list, 
                             "Top 10 Players: Total EPA-Based WAR", ep=TRUE)
top10_players_wp = plot_top10_players(positions, margins_rt, data_list, 
                             "Top 10 Players: Total WPA-Based WAR", ep=FALSE)

```



